\textbf{Computational Fuzzy Extractors}

### 2013-05-16 trunk/CompFuzzExt.tex
Working on Section 3.3

\textbf{Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.  One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.  In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.  This construction is only possible if the entropy loss due to a secure sketch leaves enough truly random bits.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.

@@

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  \lnote{I find the previous three sentences more confusing than helpful; do we really need them?  should we reword or remove?} %Our bound is a result of the Hamming bound for the space.

@@

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  The results get weaker as we consider sources with lower starter entropy.  This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed.  This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .

Both of the lower bound results arise because the reduction can ensure that \rec functions as an error-correcting code for many points of the indistinguishable distribution.  It may be possible to avoid this problem if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.  An algorithm that outputs a fresh random variable would be a computational fuzzy conductor~(see~\cite{KanukurthiR09} for the definition of a fuzzy conductor).  Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).  It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.  We leave this as an open problem.

@@

Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
\bnote{Should we mention the recent classical reduction here?}
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

@@

Thus, using the assumptions of \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.  This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-then-cextract}.

>>>>

\textbf{Alternative Approach}  Computational extractors~\cite{krawczyk2010cryptographic, barak2011leftover, dachman2012computational} have the same goal in the setting without errors.  One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.  In particular, one technique is \emph{extract-then-expand}, where the output of a randomness extractor is stretched using a pseudorandom generator.  This construction is only possible if the entropy loss due to a secure sketch leaves enough truly random bits.  
%We ask whether it is possible to avoid this loss by making whole process ``computational.''
We compare the two approaches in \secref{sec:prg based comparison}.

@@

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  Section 8.2The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

%This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  \lnote{I find the previous three sentences more confusing than helpful; do we really need them?  should we reword or remove?} %Our bound is a result of the Hamming bound for the space.

@@

The lower bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} are strongest for high entropy sources.  
%The results get weaker as we consider sources with lower starter entropy.  
This is necessary, if a source contains only codewords (of an error correcting code), no sketch is needed, and thus there is no (computational)~entropy loss.  
%For example, we can not rule out a computational secure sketch with entropy loss for low entropy sources.
%This means we cannot rule out computational sketches for other arbitrary lower entropy distributions.  
This same situation occurs when considering lower bounds for information-theoretic sketches~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08} .

Both of lower bounds arise because \rec must function as an error-correcting code for many points of any indistinguishable distribution.  It may be possible to avoid these bounds if \rec outputs a fresh random variable\footnote{If some efficient algorithm can take the output of $\rec$ and efficiently transform it back to the source $W$, the bounds of \corref{cor:rec yields sketch} and \thref{thm:imp of unp entropy} both apply.  This means that we need to consider constructions that are hard to invert~(either information-theoretically or computationally).}.  Such an algorithm is called a computational fuzzy conductor.  See~\cite{KanukurthiR09} for the definition of a fuzzy conductor.  To the best of our knowledge, a computational fuzzy conductor has not been defined in the literature, the natural definition is to replace the pseudorandomness condition in \defref{def:comp fuzzy extractor} with a HILL entropy requirement.

Our construction~(in \secref{sec:fuzzyCompExt}) has pseudorandom output and immediately satisfies definition of a computational fuzzy extractor~(\defref{def:comp fuzzy extractor}).  It may be possible to achieve significantly better parameters with a construction that is a computational fuzzy conductor~(but not a computational fuzzy extractor) and then applying an extractor.  We leave this as an open problem.

@@

Denote by $\bar{\Psi}_\alpha$ the discretized Gaussian distribution over $\Fq$ with variance $(\alpha q)^2/(2\pi)$, Regev\cite{regev2005LWE} and Peikert \cite{peikert2009latticereduction} show that, when $\chi = \bar{\Psi}_{\alpha}$, $\class{dist}$-$\lwe_{n, m, q, \chi}$ is secure if the worst-case lattice problems are hard to approximate using quantum algorithms.
%The matrix $\vA$ and secret $\vx$ are drawn from the uniform distribution, while the error term is drawn from a discretized Gaussian distribution $\bar{\Psi}_{\alpha}$.  
Furthermore, Regev \cite{regev2005LWE} shows a decision to search equivalence for $q=\poly(n)$.
%We state the decisional version in terms of unpredictability entropy~(see \defref{def:unp entropy} for the definition of unpredictability entropy and \secref{sec:LWEoverview} for an equivalence to the standard formulation of decisional LWE):

@@

Thus, using the same assumptions as \thref{thm:lossless secure conductor log}, we can obtain a computational extractor.  This means we could  build a computational fuzzy extractor using: 1) an information-theoretic secure sketch 2) a computational extractor.
We call the paradigm of running a secure sketch and using a computational extractor \emph{sketch-then-cextract}.
